### 2021-03-20 Figures/PPCA_Plant_Functional_Groups.Rmd
Edits

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$Clusters <- dat_cleaning_5$Clusters
 dat$Clusters <- as.factor(dat_cleaning_5$Clusters)
  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Clusters),size=2.5)+ scale_color_manual(values =  c("#00AFBB", "#E69F00", "#FC4E07","#000000", "darkgreen"))+ labs(color='Functional groups')

@@

 # plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),")","%", sep = "")) #XLAB
  #plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
  #plot <- plot + theme(panel.grid.minor = element_blank(),panel.grid.major = element_blank(),
   #                    panel.border = element_rect(linetype = "solid", colour = "black", size=1))

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("") +xlab("")+ylab("")

>>>>

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$Clusters <- dat_cleaning_5$Clusters
  dat$Clusters <- as.character(dat$Clusters)
  dat$Clusters[dat$Clusters=="1"] <- "A"
  dat$Clusters[dat$Clusters=="2"] <- "B"
  dat$Clusters[dat$Clusters=="3"] <- "C"
  dat$Clusters[dat$Clusters=="4"] <- "D"
  dat$Clusters[dat$Clusters=="5"] <- "E"

 dat$Clusters <- factor(dat$Clusters, levels=c("A", "B", "C", "D", "E"))

  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Clusters),size=2.5)+ scale_color_manual(values =  c("#00AFBB", "#E69F00", "#FC4E07","#000000", "darkgreen"))+ labs(color='Functional groups')

@@

  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
